A Case Study in Preserving a High Energy Physics Application

### 2014-03-02 paper.tex
content modification page 1-6

\documentclass{acm_proc_article-sp}
\usepackage{url}
\begin{document}

@@

\begin{table}[t]
    \centering
    \small
    \begin{tabular}{|l|l|r|r|r|}
        \hline
        \bf Name & \bf Location & \bf Total & \bf Named & \bf Used \\ 
        \hline
        Ntuples data    & hdfs & 24TB & 43.3GB & 20GB \\ \hline
        CMSSW binaries     & local & 1.16TB & 448.3MB & 6.3MB\\ \hline
        Tau source       & git & 73.7MB & 73.7MB & 73.7MB \\ \hline
        PyYAML binaries    & http & 52MB & 51MB & 51MB \\ \hline
        .h file       & http & 41KB & 41KB & 41KB \\ \hline
        Misc commands & PanFS & 155TB & N/A  & 1.6MB \\ \hline
        Linux commands & localFS & 110GB &  N/A & 68.3MB \\ \hline     
        Cern files & CVMFS & 7.4GB & N/A & 103MB \\ \hline
        NDCMS & NFS & 862GB & N/A & 53KB \\ \hline
        Local store & AFS &10.2GB & N/A & 34MB\\ \hline
        Total      &    & 181.1TB            & N/A & 21GB \\ \hline
    \end{tabular}
    \caption{Data and Code Used by Tau Roast}
    \label{table:size-original-real}
\end{table}

@@

The largest of these repositories is the CMS Software Distribution (CMSSW),
a carefully-curated selection of software packages which is distributed
in binary form.  Historically, CMSSW was downloaded and installed on shared
filesystems within HPC centers.  In recent years, distribution has moved to
an on-demand delivery system known as CVMFS~\cite{cvmfs}.  The content
of CMSSW is managed very carefully by a centralized team whose main goal
is to ensure that the current version of the software operates correctly
on the operating systems and architectures currently in use.  However,
preservation per se is not an objective of the group, and so there is
no guarantee that old versions of CMSSW operate in new environments,
or vice versa.

@@

Implicit dependencies include indirect software
dependencies which is necessary for the successful execution of direct software
dependencies and other implicit dependencies. For example, we know Git is one
direct software dependency from the analysis program, which further depends on
perl, python, rsync, openssh-clients and other packages. The analysis program
accesses one file called File1, which is one symbolic link file further referring to
another file named File2.
The implicit dependencies also refers to some files under {\tt /pscratch}, which is a local mount point of one PanFS with the size of 206TB.
And more importantly, the successful execution of this program greatly depends on the underlying OS and hardware platform.

@@

The size of software from each source is shown in Table~\ref{table:software-source-size}.

\subsubsection{Complexity of the Program}
Complex data and software dependencies, complex environment building process, the large size of data and software involved in the tau roast program, together with the access authority problem, determine the complexity of the program. 
In order to obtain the experimental data from the Grid, the author needs to install and config grid-control software. 
The access authority of the Grid is also necessary for the data acquisition.
The software acquisition from CMSSW, Git and HTTP and environment building process is time-consuming. The execution time of actual data analysis is about 30 minutes. However, the software acquisition and environment building time, excluding data acquisition time, is about 30 minutes, which is very close to the execution time of actual data analysis. If the acquisition of experimental data is considered, actual data analysis only occupies one small percentage of the whole time consumption.
The size of data and software dependencies further complicate the program.

@@

Even if the orginal data size referred by the program is astonishing, the size
of really used data and software is greatly smaller.
Figure~\ref{fig:data-code-size} illustrates the inputs of the tau roast program.
After the TauAnalysis procedure, the data size of Ntuples is 43.3GB, however, the atual size of really used
data in the program is 20GB.  The same trend occurs to the size of software and
other dependencies. The size of CMSSW repository is 1.16TB, the size of
packages checked out from CMSSW is 449MB, and the size of actually used CMSSW
files is only 5.2MB. 
The total size of PanFS mounted as {\tt /pscratch is 206TB}, however, the really used data from {\tt /pscratch} is only 119MB.
We compared the original size and actually used size of data and software in Table~\ref{table:size-original-real}.

@@

The stability of the Grid is relatively higher. However, the
public web resources and personal home page is not stable. Too many factors
like the termination of one web site, the graduation of the home page's author,
would result in the failure of resource access. CMSSW, which seems to be
stable, in fact, also involves stability problems. CMSSW provides different
collections of accessible versions to different architectures. Transformation
from one architecture to another may result in the failure of accessing one
certain CMSSW version. At the beginning of our reseach, cvs supported
anonymous access of CMSSW outside of CERN. However, this anonymous access has
been cancelled now.

\begin{table}
    \centering
    \begin{tabular}{|l|}
        \hline
        {\bf Version 1: Email}\\ \hline
        1. Create a CMS release,\\
            \hspace{9pt} e.g. {\tt cmsrel CMSSW\_5\_3\_11\_patch3} \\
        2. Install the BEAN packages as the instructions: \\
            \hspace{9pt} {\tt \url{https://github.com/cms-ttH/BEAN/blob/...}}\\
        3. Install grid-control: \\ 
            \hspace{9pt} {\tt svn co \url{https://ekptrac.physik.uni-ka/...}} \\
        4. INstall the TauAnalysis package: \\
           \hspace{9pt} {\tt git clone \url{https://github.com/matz-e/...}} \\
           \hspace{9pt} {\tt scram b -j32} \\
        5. Fix grid\_control.cfg and run it. \\
        6. Perform the actual tau roast program. \\ 
        \hline
        {\bf Version 2: Script}\\ \hline
        {\tt set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3)} \\
        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
        {\tt git clone \url{https://github.com/cms-ttH/BEAN.git}} \\
        {\tt wget -r \url{http://nd.edu/~abrinke1/...}} \\
        {\tt scram b -j32} \\
        {\tt wget \url{http://pyyaml.org/download/pyyaml/PyYAML...}}\\
        \#the experiment data is from HDFS \\
        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
        {\tt cmsenv}\\
        {\tt python setup.py install --user} \\
        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
        \hline
        {\bf version 3: Formulated Script} \\ \hline
        {\tt set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3)} \\
        {\tt set {\bf GIT} = (\url{https://github.com})} \\
        {\tt set {\bf PYYAML} = (\url{http://pyyaml.org})} \\
        {\tt set {\bf ND} = (\url{http://nd.edu})} \\
        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
        {\tt git clone \${\bf GIT}/cms-ttH/BEAN.git} \\
        {\tt wget -r \${\bf ND}\url{/~abrinke1/ElectronEffectiveArea.h}} \\
        {\tt scram b -j32} \\
        {\tt wget \${\bf PYYAML}/download/pyyaml/PyYAML...}\\
        \#the experiment data is from HDFS \\
        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
        {\tt cmsenv}\\
        {\tt python setup.py install --user} \\
        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
        \hline
       {\bf Version 4: Fine-Grained Toolkit}\\ \hline
        {\tt set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3)} \\
        {\tt set {\bf GIT} = (\url{https://github.com})} \\
        {\tt set {\bf PYYAML} = (\url{http://pyyaml.org})} \\
        {\tt set {\bf ND} = (\url{http://nd.edu})} \\
        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
        {\tt git clone \${\bf GIT}/cms-ttH/BEAN.git} \\
        {\tt wget -r \${\bf ND}\url{/~abrinke1/ElectronEffectiveArea.h}} \\
        {\tt scram b -j32} \\
        {\tt wget \${\bf PYYAML}/download/pyyaml/PyYAML...}\\
        \#the experiment data is from HDFS \\
        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
        {\tt cmsenv}\\
        {\tt python setup.py install --user} \\
        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
        \hline
    \end{tabular}
    \caption{Scripts of each Solution}
    \label{table:scripts}
\end{table}

@@

Figure~\ref{fig:version-evolution} illustrates the evolution history of different preservation strategies.

@@

In order to repeat Matthais's example, the new user consulted the original
author by email about the necessary work for the experiment. In response,
Matthias introduced the general workflow of his tau roast program through one long
email including notes, linux shell commands, web links. The Version 1 of
Table~\ref{table:scripts} illstrates his email.

However, this solution to repeat one experiment has three potential drawbacks.
Firstly, the experience of repeating one tau roast program through emails is
chaotic. You need to constantly jump around multiple web links. There are overlap
between the content of the email and the content of web links, which needs the
new user to merge them. Multiple communication through emails is necessary to
ensure the successful reproduction of the whole analysis. For example, the original
email refers to one environment variable called CMSSW\_base without clear
declaration, the new user needs to send one email to the original writer to
obtain its accurate value. Secondly, the necessary procedures to repeat the
experiment, including software acquisition from different sources, is complex
for the new user. In Matthias's example, the sources of software includes
CMSSW, Git, HTTP. The access of CMSSW requires the new user to be an authorized
user of CMSSW. What's more, some parts of the workflow are unrepeatable. The
third step of this experiment requires the new user to own the access authority
of the Grid.

@@

\subsection{Solution 2: Script}
One possible solution for the access authority problem of grid data is to grant the new user the authority to access gird data directly. Another possible solution is let the new user directly operate on the machine the original author used. As for the complexity of jumping between multiple web links, people may suggest that letting the original author generate one clear script including all the contents from different web links.

@@

To further separate the data and software dependencies from the actual analysis
script, we formulate the Version 2 of Table~\ref{table:scripts}  into one new version, as shown in
the Version 3 of Table~\ref{table:scripts}. Each new environment variable at the beginning part of
the script is corresponding to one dependency. All the following access to data
or software dependency will refer to its corresponding environment variable.
All the environment variables of dependencies form one map, which maintains the
target address of each dependency.

This script style may function as one new guideline to the original author of one experiment, which expresses the dependencies more clearly and expedites the preparation process to 
repeat one experiment. The introduction of the map file also reduces the workload of changing one dependency. For example, if we want to utilize one new git package to analyze the same dataset, only the change of environment variable corresponding to the original git package is necessary. Without the map file, the whole script needs to be scanned to figure out and replace all the references of the original git package.

However, each execution of the script
will involve the acquisition of software from different sources and the
building of software environment. As for accessing grid data, using the data
copy stored in the machine where Matthias executed the experiment requires the
new user to have the authority to access the machine, which complicates the
management of the original machine, even is impossible if the original machine
executes rigid user access control. Granting everyone who wants to repeat the
analysis the access authority for grid is unacceptable to system administrator.

Implication: All the data and software involved in the experiment should be
provided to the new user in the format of one self-contained package so that
the new user can avoid complex data and software acquisition and software
environment building process. In addition, the requirements of the underlying
OS and hardware should also be provided to the new user.

\subsection{Solution 4: Package}
The difficulty of data access authority acquisition enforces us to find out one
solution, in which the reproduction of the original analysis can be done
without any external dependency. That is, one independent and self-contained
package containing all the data and software dependencies is necessary.

Someone may suggest that it should be the responsibility of the original author
to generate the required package. However, letting the original author provide
the package which can be used by others to repeat the original experiment is
unrealistic. One reason is that figuring out the underlying dependencies of
each software is complex and time-consumpting and even impossible for the
original author. In this experiment, the machine used for the experiment is one
public machine of physics department, and Matthias is one common user without
root authority. The underlying OS and supporting softwares are installed and
maintained by the IT department of the university. On the other hand, the
architecture design of the required package including all the data and software
dependencies is not under the research field of physists.

To generate one self-contained and independent package for one experiment, all
the clear and implicit dependencies must be figured out firstly. The map file
of Solution 3 can provide clear data and software dependencies. As for the
implicit dependencies, directly preserving the whole OS together with the data
stored on the disk of the original machine or the data from other filesystems
mounted as local filesystems, such as HDFS and PanFS,  is not feasible. One
efficient mechanism which can figure out the really used parts of all these
filesystems is necessary. The requirements of the underlying OS and hardware
architecture can be easily found with system tools such as uname or
lsb\_release.

Then one new package including all the data and software dependencies can be generated and published. 
One packaging utility is necessary for the original author to generate the package. 
To multiplex the common data which is involved in different experiments, such as OS images and common software library, the data of different packages will be rearranged and categorized in the archive.
One description file, which includes the experiment aim, dependency list,  package size and relevant information, will be generated for each package.

@@

The relationship of different roles involved in the experiment preservation and
reproduction is shown in Figure~\ref{fig:solution3}.  The original author is
responsible for generating one package based on the successful execution
with the help of the packaging utility. Then the package, together with
its map file and description file will be uploaded into the archive. When
another scholar wants to repeat the experiment, one copy of the package and its
corresponding map file will be downloaded into the new machine.

>>>>

\documentclass{acm_proc_article-sp}
\usepackage{url}
\usepackage[flushleft]{threeparttable}
\begin{document}

@@

\begin{table}[t]
    \centering
    \small
    \begin{tabular}{|l|l|r|r|r|}
        \hline
        \bf Name & \bf Location & \bf Total & \bf Named & \bf Used \\ 
        \hline
        Ntuples data    & hdfs & 24TB & 43.3GB & 20GB \\ \hline
        CMSSW binaries     & local & 1.16TB & 448.3MB & 6.3MB\\ \hline
        Tau source       & git & 73.7MB & 73.7MB & 73.7MB \\ \hline
        PyYAML binaries    & http & 52MB & 51MB & 51MB \\ \hline
        .h file       & http & 41KB & 41KB & 41KB \\ \hline
        Misc commands & PanFS & 155TB & N/A  & 1.6MB \\ \hline
        Linux commands & localFS & 110GB &  N/A & 68.3MB \\ \hline     
        Cern files & CVMFS & 7.4GB & N/A & 103MB \\ \hline
        NDCMS & NFS & 862GB & N/A & 53KB \\ \hline
        Local store & AFS &10.2GB & N/A & 34MB\\ \hline
        Total      &    & 181.1TB            & N/A & 21GB \\ \hline
    \end{tabular}
    \begin{tablenotes}
      \small
      \item The first column illustrates the total size of each data and software source; 
            the second column illustrates the size of the named files from each source;
            the third column illustrates the size of acutally used data from each source.
            N/A denotes it is hard to figure out the named size of implicit dependencies directly.        
    \end{tablenotes}
    \caption{Data and Code Used by Tau Roast}
    \label{table:size-original-real}
\end{table}

@@

The largest of these repositories is the CMS Software Distribution (CMSSW),
a carefully-curated selection of software packages which is distributed
in binary form.  Historically, CMSSW was downloaded and installed on shared
filesystems within HPC centers.  In recent years, distribution has moved to
an on-demand delivery system known as CVMFS~\cite{blomer2011cernvm}.  The content
of CMSSW is managed very carefully by a centralized team whose main goal
is to ensure that the current version of the software operates correctly
on the operating systems and architectures currently in use.  However,
preservation is not an objective of the group, and so there is
no guarantee that old versions of CMSSW operate in new environments,
or vice versa.

@@

Implicit dependencies include indirect software
dependencies which is necessary for the successful execution of direct software
dependencies and other implicit dependencies. For example, we know Git is one
direct software dependency from the analysis program, which further depends on
perl, python, rsync, openssh-clients and other packages. The analysis program
accesses one file called File1, which is one symbolic link file further referring to
another file named File2.
The implicit dependencies also include some remote file systems mounted as local file systems, such CVMFS, AFS, NFS, PanFS and HDFS.
More importantly, the successful execution of this program greatly depends on the underlying OS and hardware platform.

@@

The first column of Table~\ref{table:size-original-real} illustrates the size of each source of data and software. The size of PanFS is as large as 155TB and the size of Ntuples data is 24TB. The total size of all the dependencies is about 181TB, which directly makes the idea of preserving the original execution environment completely impossible.

\subsubsection{Complexity of the Program}
Complex data and software dependencies, complex environment building process, the large size of data and software involved in the tau roast program, together with the access authority problem, determine the complexity of the program. 
In order to obtain the experimental data from the Grid, the author needs to install and config grid-control software. 
The access authority of the Grid is also necessary for the data acquisition.
The software acquisition from CMSSW, Git and HTTP and environment building process is time-consuming. The execution time of actual data analysis is about 20 minutes. However, the software acquisition and environment building time, excluding data acquisition time, is about 14 minutes. If the acquisition of experimental data is considered, actual data analysis only occupies one small percentage of the whole time consumption.
The size of data and software dependencies further complicates the program.

@@

Even if the orginal data size referred by the program is astonishing, the size
of really used data and software is greatly smaller.
Figure~\ref{fig:data-code-size} illustrates the inputs of the tau roast program.
After the TauAnalysis procedure, the data size of Ntuples is 43.3GB, however, the atual size of really used
data in the program is 20GB.  The same trend occurs to the size of software and
other dependencies. The size of CMSSW repository is 1.16TB, the size of
packages checked out from CMSSW is 448.3MB, and the size of actually used CMSSW
files is only 6.3MB. 
The total size of PanFS mounted as {\tt /pscratch} is 155TB, however, the really used data from {\tt /pscratch} is only 1.6MB.
The third column of Table~\ref{table:size-original-real} illustrates the size of actually used data and software from each dependency.

@@

The stability of the Grid is relatively higher. However, the
public web resources and personal home page is not stable. Too many factors
like the termination of one web site, the graduation of the home page's author,
would result in the failure of resource access. CMSSW, which seems to be
stable, in fact, also involves stability problems. CMSSW provides different
collections of accessible versions to different architectures. Transformation
from one architecture to another may result in the failure of accessing one
certain CMSSW version. At the beginning of our reseach, we can use the cvs command to
check out packages from CMSSW anonymously. However, this anonymous access has
been cancelled now.

\begin{table}
    \centering
    \begin{tabular}{|l|}
        \hline
        {\bf Version 1: Email}\\ \hline
        1. Create a CMS release,\\
            \hspace{9pt} e.g. {\tt cmsrel CMSSW\_5\_3\_11\_patch3} \\
        2. Install the BEAN packages as the instructions: \\
            \hspace{9pt} {\tt \url{https://github.com/cms-ttH/BEAN/blob/...}}\\
        3. Install grid-control: \\ 
            \hspace{9pt} {\tt svn co \url{https://ekptrac.physik.uni-ka/...}} \\
        4. INstall the TauAnalysis package: \\
           \hspace{9pt} {\tt git clone \url{https://github.com/matz-e/...}} \\
           \hspace{9pt} {\tt scram b -j32} \\
        5. Fix grid\_control.cfg and run it. \\
        6. Perform the actual tau roast program. \\ 
        \hline
        {\bf Version 2: Script}\\ \hline
        {\tt set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3)} \\
        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
        {\tt git clone \url{https://github.com/cms-ttH/BEAN.git}} \\
        {\tt wget -r \url{http://nd.edu/~abrinke1/...}} \\
        {\tt scram b -j32} \\
        {\tt wget \url{http://pyyaml.org/download/pyyaml/PyYAML...}}\\
        \#the experiment data is from HDFS \\
        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
        {\tt cmsenv}\\
        {\tt python setup.py install --user} \\
        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
        \hline
        {\bf version 3: Formulated Script} \\ \hline
        {\tt set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3)} \\
        {\tt set {\bf GIT} = (\url{https://github.com})} \\
        {\tt set {\bf PYYAML} = (\url{http://pyyaml.org})} \\
        {\tt set {\bf ND} = (\url{http://nd.edu})} \\
        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
        {\tt git clone \${\bf GIT}/cms-ttH/BEAN.git} \\
        {\tt wget -r \${\bf ND}\url{/~abrinke1/ElectronEffectiveArea.h}} \\
        {\tt scram b -j32} \\
        {\tt wget \${\bf PYYAML}/download/pyyaml/PyYAML...}\\
        \#the experiment data is from HDFS \\
        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
        {\tt cmsenv}\\
        {\tt python setup.py install --user} \\
        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
        \hline
       {\bf Version 4: Fine-Grained Toolkit - Package}\\ \hline
        {\tt set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3)} \\
        {\tt set {\bf GIT} = (\url{https://github.com})} \\
        {\tt set {\bf PYYAML} = (\url{http://pyyaml.org})} \\
        {\tt set {\bf ND} = (\url{http://nd.edu})} \\
        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
        {\tt git clone \${\bf GIT}/cms-ttH/BEAN.git} \\
        {\tt wget -r \${\bf ND}\url{/~abrinke1/ElectronEffectiveArea.h}} \\
        {\tt scram b -j32} \\
        {\tt wget \${\bf PYYAML}/download/pyyaml/PyYAML...}\\
        \#the experiment data is from HDFS \\
        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
        {\tt cmsenv}\\
        {\tt python setup.py install --user} \\
        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
        \hline
    \end{tabular}
    \caption{Scripts of each Solution}
    \label{table:scripts}
\end{table}

@@

Figure~\ref{fig:version-evolution} illustrates the evolution history of
different preservation strategies. First, an email depicting how to repeat the
experiment is used. Then, all the necessary steps to reproduce the experiment
mentioned in the mail are collected into one shell script. In order to decouple
data sources and data references, one formulated script is introduced
to express all the dependencies at the beginning of the script in the form of
environment variables. Finally, this decoupling idea is further extended into
one map file which keeps the relationship between the data reference in the
script and the actual storage location. One independent package containing all
the data and software dependencies is generated to make the reproduction
process more easier.

@@

In order to repeat Matthais's example, we consulted the original
author by email about the necessary work for the experiment. In response,
Matthias introduced the general workflow of his tau roast program through one long
email including notes, linux shell commands, web linksi, as illustrated by the Version 1 of
Table~\ref{table:scripts}.

However, this solution to repeat one experiment has three potential drawbacks.
Firstly, the experience of repeating one tau roast program through emails is
chaotic. You need to constantly jump around multiple web links. There are overlap
between the content of the email and the content of web links, which needs the
new user to merge them. Multiple communication through emails is necessary to
ensure the successful reproduction of the whole analysis. For example, the original
email refers to one environment variable called CMSSW\_base without clear
declaration, the new user needs to send one email to the original writer to
obtain its accurate value. Secondly, the necessary procedures to repeat the
experiment, including software acquisition from different sources, is complex
for the new user. In Matthias's example, the sources of software includes
CMSSW, Git, HTTP. The access of CMSSW requires the new user to be an authorized
user of CMSSW. What's more, some parts of the workflow are unrepeatable. The
third step of this experiment requires the new user to own the access authority
of the Grid and involves the analysis of AOD data with the size of about 400TB.

@@

\subsection{Solution 2: Script} One possible solution for the access authority
problem of grid data is to grant the new user the authority to access gird data
directly. Another possible solution is let the new user directly operate on the
machine the original author used. As for the complexity of jumping between
multiple web links, people may suggest that the original author
should generate one script including all the contents from different web links.

@@

To decouple data sources and data references and make the data dependencies clear, Version 2 of Table~\ref{table:scripts} is formulated into one new version, as shown in
the Version 3 of Table~\ref{table:scripts}. Each new environment variable at the beginning part of
the script is corresponding to one dependency. All the following access to data
or software dependency will refer to its corresponding environment variable.
All the environment variables of dependencies form one map, which maintains the
target address of each dependency.

This script style may function as one new guideline to the original author of
one experiment, which expresses the dependencies more clearly and expedites the
preparation process to repeat one experiment. The introduction of the map file
also reduces the workload of changing one dependency. For example, if we want
to utilize one new git package to analyze the same dataset, only the modification of
environment variable corresponding to the original git package is necessary.
Without the map mechanism, the whole script needs to be scanned to figure out and
replace all the references of the original git package.

So far, the data access authority is ignored and
the reproduction of the experiment is on the machine the original author used. 
As for grid data, using the data
copy stored in the machine where Matthias executed the experiment requires the
new user to have the authority to access the machine, which complicates the
management of the original machine, even is impossible if the original machine
executes rigid user access control. Granting everyone who wants to repeat the
analysis the access authority for grid is unacceptable to system administrator.

Implication: All the data and software involved in the experiment should be
provided to the new user in the format of one self-contained package so that
the new user can avoid 
access authority problems.
In addition, the requirements of the underlying
OS and hardware should also be figured out and provided to the new user.

\subsection{Solution 4: Fine-Grained Toolkit - Package}
The difficulty of data access authority acquisition enforces us to find out one
solution, in which the reproduction of the original analysis can be done
without any external dependency. That is, one independent and self-contained
package containing all the data and software dependencies is necessary.

Someone may suggest that it should be the responsibility of the original author
to generate the required package. However, letting the original author provide
the package. 
One reason is that figuring out the underlying dependencies of
each software is complex and time-consuming and even impossible for the
original author. In this experiment, the machine used for the experiment is one
public machine of physics department, and Matthias is one common user without
root authority. The underlying OS and supporting softwares are installed and
maintained by the IT department of the university. On the other hand, the
architecture design of the required package including all the data and software
dependencies is not under the research field of physists.

To generate one self-contained and independent package for one experiment, all
the clear and implicit dependencies must be figured out firstly. The map mechanism
of Solution 3 can provide clear data and software dependencies. As for the
implicit dependencies, directly preserving the whole OS together with the data
stored on the disk of the original machine or the data from other filesystems
mounted as local filesystems, such as HDFS and PanFS, is not feasible. One
efficient mechanism which can figure out the really used parts of all these
filesystems is necessary. The requirements of the underlying OS and hardware
architecture can be easily found with system tools such as uname or
lsb\_release.

Then one new package including all the data and software dependencies can be generated and published. 
One packaging utility is necessary for the original author to generate the package. 
To multiplex the common data which is involved in different experiments, such as OS images and common software libraries, the data of different packages will be rearranged and categorized in the archive.
One description file, which includes the experiment aim, dependency list,  package size and relevant information, will be generated for each package.

@@

The relationship of different roles involved in the experiment preservation and
reproduction is shown in Figure~\ref{fig:solution3}.  The original author is
responsible for generating one package with the help of the packaging utility. Then the package, together with
its map file and description file will be uploaded into the archive. When
another scholar wants to repeat the experiment, one copy of the package and its
corresponding map file will be downloaded into the new machine.
